Nathan Greenslit Data Analysis Project

### 2023-04-07 products/manuscript/Manuscript.qmd
Project Part 4

1.  In my `code/analysis_code/stats/3_uni_variate.qmd` code I was playing around with R2 for my linear models. Previously I have been plotting R2 onto the graphs using `stat_poly_equation()` and have also checked through `tidymodeling`. But then I came across the `stat_correlation()` command. When specifying "pearson" as the method, I get a **MUCH** higher R2 value for the models (\~0.48 to \~0.70). I have been trying to figure out what `stat_poly_equation` uses as its method and why there is such a difference. Additionally, my actual model produces the same lower R2 values (using `rsq()`) as the `stat_poly_equation()`. Is there some serious error that I am making here?

@@

    -   Why are my RMSE and AIC so high (see table under *Conclusion* section)?

@@

@@

@@

Shapiro-Wilk's tests were conducted to assess distribution of the data. Any data that did not have a normal distribution was log-transformed and the test was run again.

@@

![](images/cca_bo.jpg){width="203"}

![](images/cca_c2.jpg){width="203"}

![](images/cca_rd.jpg){width="203"}

According to the ccf plots, BO has a significant lag relationship a value of -1. In other words, dust occurs, and one day later, we see a response in copies_mL. C2 has a lag at -2, and RD at -1.

>>>>

1.  In my `code/analysis_code/stats/3_uni_variate.qmd` code I was playing around with R2 for my linear models. Previously I have been plotting R2 onto the graphs using `stat_poly_equation()` and have also checked through `tidymodeling`. But then I came across the `stat_correlation()` command. When specifying "pearson" as the method, I get a **MUCH** higher R2 value for the models (\~0.48 to \~0.70). I have been trying to figure out what `stat_poly_equation` uses as its method and why there is such a difference. Additionally, my actual model produces the same lower R2 values (using `rsq()`) as the `stat_poly_equation()`. Is there some serious error that I am making here? At least for dust and copies_mL, these are normally distributed, so this is why I am assuming Pearson's is an accepted method.

@@

    -   Why is my RMSE so high (see table under *Conclusion* section)?

@@

Thank you!

@@

\*need to add details on other environmental variables

@@

Shapiro-Wilk's tests were conducted to assess distribution of the data. Any data that did not have a normal distribution was log-transformed and the test was run again. Variables that continue to fail normality will have non-parametric tests run on them.

@@

CCF plots showed that BO has a significant lag relationship a value of -1. In other words, dust occurs, and one day later, we see a response in copies_mL. C2 has a lag at -2, and RD at -1.
